Appendix to ``Understanding both enhanced and impaired learning with enhanced plasticity: a saturation hypothesis''

### 2016-11-03 MHCpaper/MHCsupp.tex
talking about chr2

% -*- TeX -*- -*- UK -*-
% ----------------------------------------------------------------
\documentclass[10pt]{article}
%\usepackage[printfigures]{figcaps}
%\usepackage[nolists,nomarkers]{endfloat}
%Preamble:
\usepackage{a4wide}
\input{sl_preamble.tex}
\hypersetup{colorlinks,linkcolor=blue,citecolor=teal,urlcolor=teal}
\input{sl_graphics_preamble.tex}
\graphicspath{{"Figures/"}}
%
\usepackage{array}
%\newcounter{tablerow}[table]
%\newcommand{\tablerowautorefname}{row}
%\newenvironment{tabularn}[1]{\begin{tabular}{#1>{\refstepcounter{tablerow}}l}}{\end{tabular}}
%\usepackage{etoolbox}
%\AtBeginEnvironment{tabular}{\setcounter{tablerow}{0}}
\renewcommand{\figurename}{Appendix-figure}
\renewcommand{\figureautorefname}{Appendix-figure}
\DeclareCaptionLabelFormat{supp}{\textbf{#1 #2}}
\captionsetup{labelformat=supp}
% ----------------------------------------------------------------
% New commands etc.
\input{sl_definitions.tex}
\input{sl_symbols.tex}
%matrices
\newcommand{\I}{\mathbf{I}}
%vec of ones
%equilibrium distribution
\newcommand{\pr}{\mathbf{p}}
\newcommand{\eq}{\pr^\infty}
%other symbols
\newcommand{\w}{\mathbf{w}}
\newcommand{\W}{\mathbf{W}}
\newcommand{\frg}{\W^\mathrm{F}}
\newcommand{\M}{\mathbf{M}}
\newcommand{\F}{\boldsymbol{\Phi}}
\newcommand{\pot}{^{\text{pot}}}
\newcommand{\dep}{^{\text{dep}}}
\newcommand{\potdep}{^{\text{pot/dep}}}
\newcommand{\norm}{_0}
\newcommand{\inc}{_{\text{inc}}}
\newcommand{\dec}{_{\text{dec}}}
\newcommand{\incdec}{_{\text{inc/dec}}}
\newcommand{\wt}{_{\text{WT}}}
\newcommand{\ko}{_{\text{K$^\mathrm{b}$D$^\mathrm{b}$-/-}}}
\newcommand{\KO}{K$^\mathrm{b}$D$^{\mathrm{b}-/-}$}
%\newcommand{\ko}{_{\text{MHC}}}
%\newcommand{\KO}{MHC}
\newcommand{\tpre}{t_{\text{pre}}}
\newcommand{\ttrain}{t_{\text{train}}}
%\newcommand{\lmax}{_{\text{max}}}
%\newcommand{\lmin}{_{\text{min}}}
\newcommand{\modelfig}[1][a]{Figure 3#1 of the main text}
\newcommand{\datafig}[1][b]{Figure 2#1 of the main text}
% ----------------------------------------------------------------
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Title info:
\title{Appendix to ``Understanding both enhanced and impaired learning with enhanced plasticity: a saturation hypothesis''}
%
%% Author List:
%%
%\author{An Author$^a$, Another Author$^b$ and Yet Another Author$^c$\\
%%
%\small{\emph{$^a$ Address 1}}\\
%\small{\emph{$^b$ Address 2}}\\
%\small{\emph{$^c$ Address 3}}\\
%}
\date{}

@@

>>>>

% -*- TeX -*- -*- UK -*-
% ----------------------------------------------------------------
\documentclass[10pt]{article}
%\usepackage[printfigures]{figcaps}
%\usepackage[nolists,nomarkers]{endfloat}
%Preamble:
\usepackage{a4wide}
\input{sl_preamble.tex}
\hypersetup{colorlinks,linkcolor=blue,citecolor=teal,urlcolor=teal}
\input{sl_graphics_preamble.tex}
\graphicspath{{"Figures/"}}
%
\usepackage{array}
%\newcounter{tablerow}[table]
%\newcommand{\tablerowautorefname}{row}
%\newenvironment{tabularn}[1]{\begin{tabular}{#1>{\refstepcounter{tablerow}}l}}{\end{tabular}}
%\usepackage{etoolbox}
%\AtBeginEnvironment{tabular}{\setcounter{tablerow}{0}}
\renewcommand{\figurename}{Appendix-figure}
\renewcommand{\figureautorefname}{Appendix-figure}
\DeclareCaptionLabelFormat{supp}{\textbf{#1 #2}}
\captionsetup{labelformat=supp}
% ----------------------------------------------------------------
% New commands etc.
\input{sl_definitions.tex}
\input{sl_symbols.tex}
%matrices
\newcommand{\I}{\mathbf{I}}
%vec of ones
%equilibrium distribution
\newcommand{\pr}{\mathbf{p}}
\newcommand{\eq}{\pr^\infty}
%other symbols
\newcommand{\w}{\mathbf{w}}
\newcommand{\W}{\mathbf{W}}
\newcommand{\frg}{\W^\mathrm{F}}
\newcommand{\M}{\mathbf{M}}
\newcommand{\F}{\boldsymbol{\Phi}}
\newcommand{\pot}{^{\text{pot}}}
\newcommand{\dep}{^{\text{dep}}}
\newcommand{\potdep}{^{\text{pot/dep}}}
\newcommand{\norm}{_0}
\newcommand{\inc}{_{\text{inc}}}
\newcommand{\dec}{_{\text{dec}}}
\newcommand{\incdec}{_{\text{inc/dec}}}
\newcommand{\wt}{_{\text{WT}}}
\newcommand{\ko}{_{\text{K$^\mathrm{b}$D$^\mathrm{b}$-/-}}}
\newcommand{\KO}{K$^\mathrm{b}$D$^{\mathrm{b}-/-}$}
%\newcommand{\ko}{_{\text{MHC}}}
%\newcommand{\KO}{MHC}
\newcommand{\tpre}{t_{\text{pre}}}
\newcommand{\ttrain}{t_{\text{train}}}
%\newcommand{\lmax}{_{\text{max}}}
%\newcommand{\lmin}{_{\text{min}}}
\newcommand{\modelfig}[1][a]{Figure 3#1 of the main text}
\newcommand{\datafig}[1][b]{Figure 2#1 of the main text}
\newcommand{\chrfig}[1][b]{Figure 4#1 of the main text}
\newcommand{\compfig}[1][a]{Figure 4 -- figure supplement 2#1}
% ----------------------------------------------------------------
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Title info:
\title{Appendix to ``Understanding both enhanced and impaired learning with enhanced plasticity: a saturation hypothesis''}
%
%% Author List:
%%
%\author{An Author$^a$, Another Author$^b$ and Yet Another Author$^c$\\
%%
%\small{\emph{$^a$ Address 1}}\\
%\small{\emph{$^b$ Address 2}}\\
%\small{\emph{$^c$ Address 3}}\\
%}
\date{}

@@

Here, we model the effects of non-specific CF stimulation, as in \chrfig. 
It is necessary to also model the ``other'' population of synapses that compensate for the change in baseline synaptic weight of the synapses considered up to now, either due to enhanced plasticity or non-specific CF stimulation.

To be concrete, we model these other synapses as described in \compfig.
We set the relative rate of depression events for these synapses during training to $f\dep = f\dep\norm$, \ie the baseline value, so that they are unaffected by training.
For both sets of synapses during non-specific CF stimulation, we set $f\dep = > f\dep\norm$.
